---
title: "Helper's document"
---

In this file, all the code bits that need pasting into the collaborative doc will be, as well as some helpful tips to the helpers for this workshop. After a workshop has run, I'd greatly appreciate any help in improving the helper doc for future workshops, so if you have ideas let me know. If you are comfortable with GitHub, a PR directly to this repo with suggestions is highly appreciated.

## Open tabs

During the workshop, I think its a good idea for helpers to have on their computers certain tabs open at all times, so you can easily navigate to them at need

-   the collaborative document

-   [the workshop website](https://www.capro.dev/workshop_rproj/slides/00_introduction.html#/title-slide)

-   the slides the instructor is currently running through

```{r child="sections/schedule.qmd"}
```

## Frequently seen issues

### The project is doing very strange and unexpected things
Some learners will create a project folder within another project folder, this is called a nested project, and is the root of much unexpected behaviour.
  - If you see this, make sure to tell them to not do this, and to move the nested project somewhere else.
  - If several people do this, let me know, and we can have a quick discussion about it in the workshop.

### Where did the downloaded files go?  
Learners sometimes have a problem with the usethis package and where it stores the downloaded files. 

  - If you see this, have a look in their console and help them actually read what is written there. The path the files are stored to are _always_ outputed to the console.
  - By default, it will place the files in the users Home-folder or their Desktop (somewhat system dependent)
- **They don't understand what the exercise is asking them to do**
  - If you see this, have a look at the exercise and see if you can help them understand what they are supposed to do. 
  - In all the exercises, the description of the exercise is written in the `README` of the downloaded files  
  - If you can't understand the exercise either, let me know and we can have a quick discussion about it in the workshop.

## Workshop progression

In this section, we have anything that is related to the workshop as it is progressing. Each section has its own subtitle here, and these should also match sections in the collaborative document. This way, helpers can easily navigate to the relevant section in the helper document.

### EduCloud flavour

Slides: [https://www.capro.dev/workshop_rproj/slides/educloud_prep.html#/title-slide](https://www.capro.dev/workshop_rproj/slides/educloud_prep.html#/title-slide)

This section is only when we run the course on EduCloud.

The project for the course i `ec306`, but that does not really matter. We wont by default be using the project space.


#### What you should be doing

- Make sure people are able to log into EduCloud On demand  
- Make sure people are able to start an RStudio server  
- If these things are unavailable to them, make sure they have a local installation of R and RStudio on their computer  

#### Exercise

Learners will first go to open on demand, and start an RStudio server https://ondemand.educloud.no/pun/sys/dashboard

### Introduction

Slides: [https://www.capro.dev/workshop_rproj/slides/00_introduction.html](https://www.capro.dev/workshop_rproj/slides/00_introduction.html)

The introduction is meant to provide a basis of what we will be talking about during the workshop, to set expectations and provide everyone with an equal frame of reference.

#### What you should be doing

-  Make sure everyone is able to access the collaborative document  
-  Make sure everyone is able to access the slides/website  
-  Keep an eye on the doc for anonymous questions  
-  If there are questions, make sure they are answered either in the doc or by me if you think its a good question to take up in the workshop  

At the end there is an exercise to get people to explore their R installation and get familiarized with it.

#### Exercise: Explore your R installation

Learners should run this code:

```{r, echo=TRUE, eval=FALSE}
install.packages("usethis")
library(usethis)
use_course("rstats-wtf/wtf-explore-libraries")
```

The exercise is singular, but has three flavours (as most exercises for this course has).

-   **solution**: provides the solution to the exercise, for novices
-   **comfy**: provides example code to run, for intermediates
-   **spartan**: provides no example code, for experts

I will always walk through the solution once the exercise is done.

### Project Oriented workflow

Slides: [https://www.capro.dev/workshop_rproj/slides/01_project-oriented.html#/title-slide](https://www.capro.dev/workshop_rproj/slides/01_project-oriented.html#/title-slide)

This section is about what project oriented workflows are and why we should adopt them. 
There are a fair few links to various important resources, that learners might want into the collaborative document, if they don't have the slides up while we instruct.

#### What you should be doing

-  If they ask for link from the slides, either paste the link to the slides, or the links them selves  
-  Keep an eye on the doc for anonymous questions    
-  If there are questions, make sure they are answered either in the doc or by me if you think its a good question to take up in the workshop   

#### Exercise

The exercise is to create a new project, in the folder they downloaded in the previous exercise. 
Meaning, they should create a project in an existing folder, either through the RStudio GUI, or through the R console.

They need to change this path to where the folder is 

`usethis::create_project("/path/to/folder")`

OR do

`File -> New Project -> Existing Directory`

### File naming

Slides: [https://www.capro.dev/workshop_rproj/slides/02_file-naming.html#/title-slide](https://www.capro.dev/workshop_rproj/slides/02_file-naming.html#/title-slide)

This section is all about names, and here we have no exercises, but rather some verbal discussion and shout-outs to the slides. Here the focus is to get them thinking about what file names are good and why some file names are worse.

#### What you should be doing

-  Keep an eye on the doc for anonymous questions    
-  If there are questions, make sure they are answered either in the doc or by me if you think its a good question to take up in the workshop  
-  In particular, pay attention to anything related to file naming or silent discussions about these that are not voiced openly.
  - If you overhear someone discussing something interesting, ask politely if they would like to share their thoughts with the group, or if you can share some of it for them.

### Project Structure

Slides: [https://www.capro.dev/workshop_rproj/slides/03_project-structure.html#/title-slide](https://www.capro.dev/workshop_rproj/slides/03_project-structure.html#/title-slide)

In the project structure section, we talk about what constitutes a good project structure. 
There is no singular correct answer to this, but there are guidelines that are good to discuss and talk about.
Mostly we here talk about how splitting a project into several parts is better than having one large singular script.

#### What you should be doing

-  Keep an eye on the doc for anonymous questions    
-  If there are questions, make sure they are answered either in the doc or by me if you think its a good question to take up in the workshop 
-  Most researchers work in the "monolith" type of project structure, so this section will feel very unfamiliar to them and be a new consept about how to work.
   - If you see people struggling with this, or if you see people discussing this, ask them if they would like to share their thoughts with the group, or if you can share some of it for them.

#### Exercise

In this exercise at the end, they are again instructed to download some exercise materials. 
This time, they should read the README for further instructions on what they should be doing during the exercise.

```{r, echo=TRUE, eval=FALSE}
library(usethis)
# saves project on desktop by default for most users
use_course("rstats-wtf/wtf-packages-report")
# use_course("rstats-wtf/wtf-packages-report", destdir = "my/new/location")
# can alternatively download from 
# https://github.com/rstats-wtf/wtf-packages-report
```

They should familiarise themselves with the project structure and how its set up. 
Then run sequentially through the three exercises in the `R/` folder. 
The expectation here is that most people will not be able to finish it all during the time allotted, but that is fine. 
We just have enough material so even experts can feel challenged.

### Package management

Slides: [https://www.capro.dev/workshop_rproj/slides/04_package-management.html#/title-slide](https://www.capro.dev/workshop_rproj/slides/04_package-management.html#/title-slide)

This section is all about package management, and how to manage packages in a project. 
This is by far the most advanced subject we are covering, and I expect some to feel a little overwhelmed. 
Nonetheless, this is a section a lot of people really appreciate, and even novices will be able to take away things to remember in the future when they get more comfortable. 
Package management is a known sore point for R users, particularly on shared resources like EduCloud!

Here we talk about why package management in R can be tricky, why we should care, and offer the current best practice solution.

#### What you should be doing

-  Keep an eye on the doc for anonymous questions    
-  This is an advanced topic, and I expect a lot of questions, please help me pick up on these and answer them as we go along. 

#### Exercise

The exercise here is a little different than what we have done before. 
It still contains the three flavours, but requires the learners to

-   go through the exercises,
-   make a note of the results,
-   then initiate the package manager,
-   redo the exercise, noting the difference between the two

```{r, echo=TRUE, eval=FALSE}
library(usethis)
# saves project on desktop by default for most users
use_course("capro-uio/wtf-explore-renv")
# use_course("capro-uio/wtf-explore-renv", destdir = "my/new/location")
# can alternatively download from 
# https://github.com/capro-uio/wtf-explore-renv

```


Here, we want to make a point of how the package manager changes where and how packages are stored.

### Ending the workshop

At the end we open for general questions, and try to walk through whatever the learners want to cover, as time allows.
We focus on providing them links to the relevant resources, and try to make sure they know where to go to find more information.

The collaborative document will contain a link to a post-workshop survey in most cases. 
Help the instructor remember to make a notice of this and ask the learners to fill it out.
We also usually ask for positive and constructive feedback written on the sticky notes, as a quick feedback to the instructor.

