---
output: github_document
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# R Project Management

<!-- badges: start -->

<!-- badges: end -->

This repo contains materials and resources for a 1-day course in project management in R. It is a quarto website, and as such adhered to basic [quarto conventions](https://quarto.org/docs/websites/).

-   `slides` contains the slides for the course
-   `sections` contains the child quarto sections reused in the materials
-   `_quarto.yaml` contains the quarto configuration for the course
-   `index.qmd` contains the course homepage

The repo uses [renv](https://rstudio.github.io/renv/) to manage package dependencies. To install the packages used in this course, run `renv::restore()` from the project root.

```{r child="sections/intro.qmd"}
```

```{r child="sections/aims.qmd"}
```

```{r child="sections/schedule.qmd"}
```

```{r child="sections/prep.qmd"}
```

```{r child="sections/resources.qmd"}
```
