---
title: "Introduction"
subtitle: "Working in R and RStudio"
author: "Athanasia Mo Mowinckel"
footer:  "Workshop Overview"
#logo: "img/wtf-logo-square-transparent.png"
format: 
  revealjs: 
    height: 900
    width: 1600
    theme: 
      - night
      - capro-reveal.scss
    highlight-style: a11y
    transition: fade
    slide-number: true
    chalkboard: true
editor: visual
execute:
  freeze: auto
---

```{r}
library(countdown)
```

# CAPRO

We specialize in data processing and capture of large life science data for social sciences and humanities

::: footer
<https://www.capro.dev/>
:::

# CAPRO

::: {style="text-align: right;"}
-   Data flow and processing

-   Data capture

-   Project data management

-   Registry data handling

-   HPC analyses
:::

::: footer
<https://www.capro.dev/>
:::

# Meet your neighbors

```{r}
countdown(
  color_background = "#CC4C4C",
  color_text = "#d2d2d2",
  color_finished_background = "#CC4C4C",
  minutes = 3,
  bottom = "0%"
  )
```

# Pre-workshop checklist

<br><br>

<https://github.com/posit-conf-2023/wtf#prework>

# Asking for help

::: columns
::: column
::: {data-id="box1" style="background: #CC4C4C; width: 500px; height: 150px; margin: 20px; padding: 20px; padding-top: 70px; text-align: center;"}
I'm stuck or need help
:::
:::

::: column
::: {data-id="box2" style="background: #37765d; width: 500px; height: 150px; margin: 20px; padding: 20px; padding-top: 70px; text-align: center;"}
All good, ready to move on
:::
:::
:::

# Completion survey

<br>

At the conclusion of the workshop, please submit <https://pos.it/conf-workshop-survey>.

<br>

Your feedback is crucial! Data from the survey informs curriculum and format decisions for future conf workshops, and we really appreciate you taking the time to provide it.

# Go here now

<br><br>

<https://github.com/posit-conf-2023/wtf#schedule>
